Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-11 extended_catalog/paper/extended_catalog.tex
stuff

For extended sources with an assumed radially symmetric shape,
we use a semi-analytic calculation to speed up the calculation of
the expected photon distribution. The expected photon 
distribution can be written as
\begin{equation}
  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') d A'.
\end{equation}
For the LAT, the PSF can be parameterized by a {\em King function}
\begin{equation}
  \text{PSF}(\vec r) = 
  \frac{1}{2\pi\sigma^2}
  \left(1-\frac{1}{\gamma}\right)
  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
\end{equation}
where $\sigma$ and $\gamma$ are free parameters
(\cite{matthew_kerr_thesis}).  For radially symmetric extended sources,
the angular part of the integral can be done analytically
\begin{align}
  \text{PDF}(u) & = \int_0^\infty \sigma^2 dv 
  I_\text{src}(v) 
  \int_0^{2\pi} d\phi' 
  \text{PSF}(\sqrt{2\sigma^2(u+v-2\sqrt{uv}\cos(\phi-\phi'))})
  \\
  & = \int_0^\infty dv
  I_\text{src}(v) 
  \left(\frac{\gamma-1}{\gamma}\right)
  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
\end{align}
where $u=(r/\sigma)^2/2$, $v=(r'/\sigma)^2/2$, and ${}_2F_1$ is the
Gaussian hypergeometric function.  This convolution formula is used by
\pointlike, reducing the calculation of the expected photon distribution
to a single numerical integral.

@@

We found good agreement between the two methods. For the new extended
source candidates, table~\ref{alt_diff_model_results} shows a
comparison of the test statistic \ts and \tsext computed using \pointlike
and \gtlike.  Unless explicitly mentioned, all \ts, \tsext, and spectral
parameters were calculated using \gtlike using \pointlike's positions
and extensions.

@@

We define \tsinc as twice the increase in \loglikelihood fitting the
region as two point sources compared to fitting the region as one point
source: 
\begin{equation}
  \tsinc=2\times(\loglikelihood_\text{2pts}-\loglikelihood_\text{ps}).
\end{equation} 
\tsinc can not be directly compared to \tsext to see which
model is more significant because the models are not nested
(\cite{statistics_with_care}). Even though the comparison of \tsext with
\tsinc is not a calibrated test, we find the cases $\tsinc \ll \tsext$
or $\tsinc\gg\tsext$ suggestive and we only consider a source to be
extended if $\tsext>\tsinc$.

Like extended sources described in section~\ref{gtlike_crosscheck},
the spectrum of the two point sources can be refit using \gtlike.
We quote the spectral values obtained from \gtlike using the best fit
positions found using \pointlike.  For the extended candidates found
by our search, we computed both \tsext and \tsinc.  The results are
presented in table~\ref{dual_localization_results}.

@@

We tested two different models for the
spatial shape, either a two dimensional Gaussian
\begin{equation}\label{gauss_pdf}
  I(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}\label{disk_pdf}
  I(x,y)=
  \begin{cases}
    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
    0                      & x^2+y^2>\sigma^2
  \end{cases}
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF look similar.  Figure~\ref{compare_disk_gauss}
demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
a uniform disk and Gaussian spatial model of size 0.5\deg.\footnote{To
allow a valid comparison between Gaussian and disk shaped morphologies,
we define the source size for this test as the radius containing
68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
is defined in equation~\ref{gauss_pdf} and
equation~\ref{disk_pdf} respectively.} This plot shows that we are
not very sensitive to probing the exact structure of an extended source.
In the search for extended sources, we therefore use only a uniform
disk as our spatial extension shape. We then quote the radius of the
disk edge as the size of the source.

@@

We used the simulation setup described in
section~\ref{monte_carlo_validation}, but instead simulated extended
sources with a uniform radially symmetric disk spatial model and
instead over the actual two year time interval.  For each extension and
spectral index, we picked a flux range which bracketed $\tsext=16$. We
then picked ten flux points in this range and repeatedly simulated
and then performed extension tests of the simulated extended source.
We calculated $\langle\tsext\rangle=16$ by fitting a line to the flux
and $\tsext$ values.

@@

\section{Extended Source Search Method}

@@

For the remaining candidates, 
we took the spatial and spectral model found using \pointlike and
redetermined the spectral 
parameters using
\gtlike.  We used 
the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
ROI with a pixel size of 0.03\deg.
We obtained a second measure of \tsext from \gtlike for the extension
and position of the source as determined by \pointlike.
We only considered a source to be significantly extended if $\tsext>16$ with
both \pointlike and \gtlike.  For the new extended source candidates,
table~\ref{alt_diff_model_results} shows a comparison of of \tsext for
\gtlike and \pointlike.

@@

We estimate a second systematic error on the extension of a source
due to uncertainty in the model of the Galactic diffuse emission by
using an alternative diffuse model. The alternative model was based on
the GALPROP\footnote{GALPROP is a software package for calculating the
Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
in the Galaxy. See \url{http://galprop.stanford.edu/} for details and
references} model used in the LAT analysis of the isotropic diffuse
emission (\cite{isotropic_lat}).  With this model, we independently fit
along with the point and diffuse sources in the region seven HI rings,
seven HII rings, the inverse component, the E(B-V) residual, and the
isotropic component of the background emission.  All told, we fit in
the region 18 diffuse templates.  This same crosscheck was used in the
LAT Collaboration's analysis of RX J1713.7-3946 (\cite{rx_j1713_lat}).

It is not expected that this diffuse model is more physical.
But adding degrees of freedom to the background model can remove
likely spurious sources that correlate with features in the Galactic
diffuse emission.  Therefore, this tests systematics that may be
due to incorrect modeling of the diffuse emission in the region.
The results of this fit for the new extended source candidates are shown
in table~\ref{alt_diff_model_results}. There is good agreement between
the \ts using the standard and alternative diffuse models, suggesting
that the sources are robust against features in the diffuse model.

@@

% 3 PWN
Three pulsar wind nebula Vela X, MSH 15-52, and HESS\,J1825-137 were
included in 2FGL (\cite{velax,msh1552,fermi_hess_j1825}).  Using photons
with energy above 10 \gev, we significantly detected the extension of
HESS\,J1825-137.  To improve the model of this source, we removed the
nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
source.  To avoid the nearby pulsar PSR J1509-5850, MSH 15-52 must be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH 15-52 to be consistent with the published
size with an extension significance of \tsext=6.5.

% failed to detect vela x + cen a
Our analysis was unable to resolve Vela X which would have required first
removing the pulsed photons from the Vela pulsar. This is beyond the
scope of this paper.  Our analysis also failed to detect a significant
extension for the Centaurus A Lobes (\cite{cen_a_lat}). This is because
the source's emission is significantly more complicated than a uniform
radially symmetric Disk.

Our analysis of these sources is summarized in
table~\ref{known_extended_sources}.  This table includes the best fit
position and extension of these sources when fitting them with a radially
symmetric uniform disk spatial model.  It also includes the best fit
spectral parameters for each source.  The position and extension of Vela
X and the Centaurus A Lobes are included in this list for completeness.

\section{Test of 1LAC Sources}
\label{test_1lac_sources}

To validate our method, we test associated AGN for extension.  \gev
emission from AGN is believed to comes from the core of supermassive
blackholes in small regions in the core of distant galaxies. Therefore AGN
are not expected to be spatially resolvable and provide a good calibration
source to demonstrate the efficacy of our tool. Nevertheless, it would
be interesting if AGN could be spatially resolved and there are theories
that predict this (\cite{pair_halo_paper}).

Following 1FGL, the LAT collaboration published a list of sources that
had a high probability association with AGN (\cite{first_agn_cat}).
1FGL had 709 1FGL sources associated with 671 distinct AGN at high
latitude ($|b|>10\deg$).  An upcoming publication by the LAT collaboration
using two years of data and the 2FGL catalog associates 1017 2FGL sources
with AGN.  To avoid systematic problems with AGN classification, we
selected the 815 AGN which made it into the clean AGN sample.  An AGN
association is considered clean only if it has a high probability
of association $P\ge 80\%$, if it is the only AGN associated with the
catalog source, and if there are no flags on the source in 2FGL. These
last two conditions are important for our analysis. Source
confusion may look like a spatially extended source and flagged catalog
sources may correlate with unmodeled structure in the diffuse emission.

Of the 815 clean AGN, we select 775 of these 2FGL sources which
are significant above 1 \gev and fit each of them for extension.
A histogram of the \tsext values computed for these AGN is shown in
figure~\ref{agn_ts_ext}. Overlaid on the plot is the $\chi^2/2$
distribution of equation~\ref{ts_ext_distribution}.
The \tsext distribution for AGN shows good
agreement with the theoretical distribution.  Two sources had $\tsext>9$.
One was due to incorrectly pruning a nearby catalog sources and the
other was due to a failure of convergence of the point hypothesis.
This result demonstrates that we can use \tsext as a measure of the
statistical significance of the detection of the extension of a source.

We should clarify that the LAT PSF used in this study was determined
empirically by fitting the observed shape of bright AGN (see
section~\ref{systematic_errors_on_extension}). Finding that the AGN we
test are not extended is not surprising. Trying to look for the extension
of AGN would require a more specialized analysis.

@@

Nine extended sources not include in 2FGL were found using this search.
Three were found in our search using 1-100 \gev photons and 
six were found in our search using 10-100 \gev photons.  
The fit properties of these nine sources is summarized in
table~\ref{new_ext_srcs_table}.  This table includes for each source
the best fit position, extension, spectrum, source significance, and
significance of extension.

For the new extended sources, table~\ref{dual_localization_results}
presents a test for source confusion by fitting the region
as two point sources. The table compares \tsext to \tsinc and
summarizes the positions and spectra of the two sources. 
Table~\ref{alt_diff_model_results} contains the fit extensions
using the alternate PSF and Galactic diffuse model described in
section~\ref{systematic_errors_on_extension}.

@@

The two year catalog source 2FGL\,J0823.0-4246 was found 
using 1-100 \gev photons to have an 
extension of $0.37\deg\pm0.03\deg\stat\pm0.02\deg\sys$ 
with an extension
significance of $\tsext=46.3$.  The source was fit to a position of
$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source.  This source is coincident with the one year
catalog source 1FGL\,J0823.3-4248.

@@

The two year catalog source 2FGL\,J1627.0-2425c was found 
using 1-100 \gev photons to have an 
extension of $0.41\deg\pm0.05\deg\stat\pm0.02\deg\sys$ 
with an extension significance of $\tsext=31.1$. 
The best fit position is $(l,b)=(353.08\deg, 16.78\deg)$.
This source is coincident with the one year catalog source 1FGL\,J1628.6-2419c.
A counts map showing this source is
seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=20.0$
is smaller than \tsext, we conclude that this is an extended source.

@@

The two year catalog source 2FGL\,J1712.4-3941 was found using 1-100 \gev
photons to have an extnesion $0.56\deg\pm0.04\deg\stat\pm0.02\deg\sys$
with an extension significance of $\tsext=39.6$.  This source was
fit to a position of $(l,b)=(347.25\deg,-0.54\deg)$.  The source
is coincident with the one year catalog source 1FGL\,J1711.7-3944c.
Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.

@@

The two year catalog source 2FGL\,J0851.7-4635 was found 
using 10-100 \gev photons to have an
extension of $1.13\deg\pm0.08\deg\stat\pm0.05\deg\sys$ 
with an extension
significance of $\tsext=87.2$.  The source was fit to a position of
$(l,b)=(266.29\deg,-1.43\deg)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

@@

To get a good fit of the source, we had to remove thee nearby catalog
sources 2FGL\,J0853.5-4711, 2FGL\,J0848.5-4535, and 2FGL\,J0855.4-4625
which are part of the extended source.  In addition, we relocalized
the position of the nearby catalog source 2FGL\,J0854.7-4501 to
$(l,b)=(266.24\deg,0.49\deg)$ to better fit its position at high energies
in the presence of of the extended source.  In addition, we removed the
further away catalog sources 2FGL\,J0858.0-4815 and 2FGL\,J0901.7-4655
because they were not significant above 10 \gev.  After modifying
the region, we found that \tsinc=16.1 which is less than \tsext so we
conclude that the source is extended These modifications are shown in
figure~\ref{Vela_Jr}.

@@

The two year catalog source 2FGL\,J1615.0-5051 was found using 10-100 \tev
photons to have an extension of $0.33\deg\pm0.04\deg\stat\pm0.01\deg\sys$
with an extension significance of \tsext=16.3.  The source
was fit to a position of $(l,b)=(332.38\deg,-0.14\deg)$.
This source is coincident with the one year catalog source
1FGL\,J1613.6-5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
of this source.

@@

2FGL\,J1615.2-5138 is spatially coincident with the extended
\tev source HESS\,J1616-508 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured a Gaussian
extension $0.136\pm 0.008$ when fitting the source with an elliptical
Gaussian spatial model.  This size corresponds to a 68\% containment
radius of $\rsixeight=0.21\deg\pm0.01\deg$. This size is comparable to the LAT
size $\rsixeight=0.27\deg\pm0.03\deg$ (see section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.

@@

The two year catalog source 2FGL\,J1615.2-5138 was found using 10-100 \gev
photons to have an extension of $0.42\deg\pm0.03\deg\stat\pm0.01\sys$
with an extension significance of \tsext=48.0.  The source was fit to a
position of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
with the one year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
J1615.2-5138 is close to 2FGL\,J1615.0-5051, the same model described
in section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
sources. Both sources can be seen in figure~\ref{1FGL_J1613.6-5100c}.
For 2FGL\,J1615.2-5138, \tsinc=37.0 which is less than \tsext so we
conclude that the source is extended.

@@

The two year catalog source 2FGL\,J1632.4-4753c was found 
using 10-100 \gev photons to
have an extension of $0.44\deg\pm0.04\deg\stat\pm0.03\deg\sys$ 
with an extension
significance of \tsext=64.5.  The source was fit to a position of
$(l,b)=(336.41\deg,0.22\deg)$.  This source is coincident with the one
year catalog source 1FGL\,J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
shows a counts map of this source.

@@

This extended source is spatially coincident with the extended
\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478 are
overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a Gaussian extension of
$\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the semi-major and semi-minor
axes when fitting the source with an elliptical Gaussian spatial model.
This corresponds to a 68\% containment size $\rsixeight=0.31\deg\pm0.08\deg$
and $0.09\pm0.06$ along the semi-major and semi-minor axis. This
size is consistent with the LAT size $\rsixeight=0.36\deg\pm0.04\deg$.
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1635.4-4717c
connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478 and most
likely corresponds to the same emission process

@@

The two year catalog source 2FGL\,J1837.3-0700c was found 
with 10-100 \gev photons 
to have an extension
of $0.35\deg\pm0.08\deg\stat\pm0.03\deg\sys$ 
with an extension
significance of $\tsext=18.8$.  The source was fit to a position of
$(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
year catalog source 1FGL\,J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
shows a counts map of this source.

@@

      \tsext was computed with \gtlike assuming the best fit uniform
      disk spatial model from \pointlike.  \glon and \glat are Galactic

@@

      $\sigma$ is the edge of the best fit uniform disk spatial model.

@@

      Lobes were not fit by our anaysis but are include for completeness

>>>>

For extended sources with an assumed radially symmetric shape,
we use a semi-analytic calculation to speed up the calculation of
the expected photon distribution. The expected photon 
distribution can be written as
\begin{equation}
  \text{PDF}(\vec r) = \int  \text{PSF}(|\vec r - \vec r'|)I_\text{src}(\vec r') r'^2 dr' d\phi'
\end{equation}
For the LAT, the PSF can be parameterized by a {\em King function}
\begin{equation}
  \text{PSF}(r) = 
  \frac{1}{2\pi\sigma^2}
  \left(1-\frac{1}{\gamma}\right)
  \left(1+\frac{u}{\gamma}\right)^{-\gamma},
\end{equation}
where $u=(r/\sigma)^2/2$ and $\sigma$ and $\gamma$ are free parameters
(\cite{matthew_kerr_thesis}).  For radially symmetric extended sources,
the angular part of the integral can be done analytically
\begin{align}
  \text{PDF}(u) & = \int_0^\infty r'^2 dr'
  I_\text{src}(v) 
  \int_0^{2\pi} d\phi' 
  \text{PSF}(\sqrt{2\sigma^2(u+v-2\sqrt{uv}\cos(\phi-\phi'))})
  \\
  & = \int_0^\infty dv
  I_\text{src}(v) 
  \left(\frac{\gamma-1}{\gamma}\right)
  \left( \frac{\gamma}{\gamma + u + v}\right)^\gamma 
  \times {}_2F_1 \left(\gamma/2,\frac{1+\gamma}{2},1,\frac{4uv}{(\gamma+u+v)^2}\right).
\end{align}
where $v=(r'/\sigma)^2/2$ and ${}_2F_1$ is the Gaussian hypergeometric
function.  This convolution formula reduces the expected photon
distribution to a single numerical integral.

@@

We found good agreement between the two methods.  
Unless explicitly mentioned, all \ts, \tsext, and spectral
parameters were calculated using \gtlike using \pointlike's positions
and extensions.

@@

We define \tsinc as twice the increase in \loglikelihood fitting the
region as two point sources compared to fitting the region as one point
source: 
\begin{equation}
  \tsinc=2\times(\loglikelihood_\text{2pts}-\loglikelihood_\text{ps}).
\end{equation} 
\tsinc can not be directly compared to \tsext to see which
model is more significant because the models are not nested
(\cite{statistics_with_care}). Even though the comparison of \tsext with
\tsinc is not a calibrated test, we find the cases $\tsinc \ll \tsext$
or $\tsinc\gg\tsext$ suggestive and we only consider a source to be
extended if $\tsext>\tsinc$.
Like extended sources described in section~\ref{gtlike_crosscheck},
the spectrum of the two point sources can be refit using \gtlike.
We quote the spectral values obtained from \gtlike using the best fit
positions found using \pointlike.

@@

We tested two different models for the
spatial shape, either a two dimensional Gaussian
\begin{equation}\label{gauss_pdf}
  I(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}\label{disk_pdf}
  I(x,y)=
  \begin{cases}
    \frac{1}{\pi\sigma^2} & x^2+y^2\le\sigma^2 \\
    0                      & x^2+y^2>\sigma^2
  \end{cases}
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF look similar.  Figure~\ref{compare_disk_gauss}
demonstrates this by showing $I_\text{src}$, the PSF, and the PDF for
a radially symmetric uniform and Gaussian surface brightness of size 0.5\deg.\footnote{To
allow a valid comparison between Gaussian and disk shaped morphologies,
we define the source size for this test as the radius containing
68\% of the intensity ($\rsixeight$).  $\rsixeight_\text{,Gaussian}=1.51\sigma$
and $\rsixeight_\text{,disk}=0.82\sigma$ where $\sigma$
is defined in equation~\ref{gauss_pdf} and
equation~\ref{disk_pdf} respectively.} This plot shows that we are
not very sensitive to probing the exact structure of an extended source.
In the search for extended sources, we therefore use only a uniform
disk as our spatial extension shape. We then quote the radius of the
disk edge as the size of the source.

@@

We used the simulation setup described in
section~\ref{monte_carlo_validation}, but instead simulated extended
sources with a radially symmetric uniform surface
brightness and
instead over the actual two year time interval.  For each extension and
spectral index, we picked a flux range which bracketed $\tsext=16$. We
then picked ten flux points in this range and repeatedly simulated
and then performed extension tests of the simulated extended source.
We calculated $\langle\tsext\rangle=16$ by fitting a line to the flux
and $\tsext$ values.

@@

\section{Extended Source Search Method}
\label{extended_source_search_method}

@@

For the remaining candidates, 
we took the spatial and spectral model found using \pointlike and
redetermined the spectral 
parameters using
\gtlike.  We used 
the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
ROI with a pixel size of 0.03\deg.
We obtained a second measure of \tsext from \gtlike for the extension
and position of the source as determined by \pointlike.
We only considered a source to be significantly extended if $\tsext>16$ with
both \pointlike and \gtlike.

@@

We estimate a second systematic error on the extension of a source
due to uncertainty in the model of the Galactic diffuse emission by
using an alternative diffuse model. The alternative model was based on
the GALPROP\footnote{GALPROP is a software package for calculating the
Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
in the Galaxy. See \url{http://galprop.stanford.edu/} for details and
references} model used in the LAT analysis of the isotropic diffuse
emission (\cite{isotropic_lat}).  
The intensities of various contributions to the galactic
diffuse emission are then fitted individually using a spatial
distribution of the intensities within the ROI 
as predicted by the model.
We distinguish contributions from CR interactions with
the molecular hydrogen, the atomic+ionized hydrogen,
residual gas traced by dust (\cite{isabelle_dark_gass}),
and the interstellar radiation field. We further
split the contributions from interactions with molecular
and atomic hydrogen to the
Galactic diffuse emission according
to the distance from the Galactic center in
which they are produced. Hence, we replace
the standard diffuse emission model by 18
individually fitted templates to describe individual
components of the diffuse emission.
A similar crosscheck was used in the
LAT Collaboration's analysis of RX J1713.7-3946 (\cite{rx_j1713_lat}).

It is not expected that this diffuse model is superior to the standard
LAT model.  But adding degrees of freedom to the background model can
remove likely spurious sources that correlate with features in the
Galactic diffuse emission.  Therefore, this tests systematics that may
be due to incorrect modeling of the diffuse emission in the region.

@@

% 3 PWN
Three pulsar wind nebula Vela X, MSH 15-52, and HESS\,J1825-137 were
included in 2FGL (\cite{velax,msh1552,fermi_hess_j1825}).  Using photons
with energy above 10 \gev, we significantly detected the extension of
HESS\,J1825-137.  To improve the model of this source, we removed the
nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
source.  To avoid confusion with the nearby bright pulsar PSR J1509-5850, MSH 15-52 must be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH 15-52 to be consistent with the published
size with an extension significance of \tsext=6.5.

% failed to detect vela x + cen a
Our analysis was unable to resolve Vela X which would have required first
removing the pulsed photons from the Vela pulsar. This is beyond the
scope of this paper.  Our analysis also failed to detect a significant
extension for the Centaurus A Lobes (\cite{cen_a_lat}). This is because
the source's emission is significantly different from a uniform
radially symmetric Disk.

Our analysis of these sources is summarized in
table~\ref{known_extended_sources}.  This table includes the best fit
position and extension of these sources when fitting them as disk-shaped
sources with a radially symmetric uniform surface brightness. It also
includes the best fit spectral parameters for each source.  The position
and extension of Vela X and the Centaurus A Lobes are included in this
list for completeness.

\section{Test of 2LAC Sources}
\label{test_2lac_sources}

To validate our method, we test LAT sources associated with AGN for
extension.  \gev emission from AGN is believed to originate from the cores
of kpc-scale jets of distant galaxies.  Therefore AGN are not expected
to be spatially resolvable and provide a good calibration source to
demonstrate the efficacy of our tool.  We note that mpc-scale $\gamma$-ray
halos around AGNs have been hypothesized (\cite{pair_halo_paper}) which
could be resolved by the LAT However, no such halo has been discovered
in the LAT data so far.

Following 1FGL, the LAT collaboration published a list called 1LAC
of sources that
had a high probability association with AGN (\cite{first_agn_cat}).
1FGL had 709 1FGL sources associated with 671 distinct AGN at high
latitude ($|b|>10\deg$).  An upcoming publication by the LAT collaboration
will produce a second list 2LAC. 2LAC 
uses the 2FGL catalog and associates 1017 2FGL sources
with AGN.  To avoid systematic problems with AGN classification, we
selected 815 out of the 1017 AGN which made it into the clean AGN sub-sample.  An AGN
association is considered clean only if it has a high probability
of association $P\ge 80\%$, if it is the only AGN associated with the
catalog source, and if there are no flags on the source in 2FGL. These
last two conditions are important for our analysis. Source
confusion may look like a spatially extended source and flagged catalog
sources may correlate with unmodeled structure in the diffuse emission.

Of the 815 clean AGN, we select 775 of these 2FGL sources which
are significant above 1 \gev and fit each of them for extension.
A histogram of the \tsext values computed for these AGN is
shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is the
$\chi^2/2$ distribution of equation~\ref{ts_ext_distribution}.
The \tsext distribution for AGN shows good agreement with the
theoretical distribution.  Two sources had $\tsext>9$.  One was due
to incorrectly automatically removing a nearby catalog sources (see
section~\ref{extended_source_search_method}) and the other was due to a
failure of convergence of the point hypothesis.  This result demonstrates
that we can use \tsext as a measure of the statistical significance of
the detection of the extension of a source.

We should clarify that the LAT PSF used in this study was determined
empirically by fitting the observed shape of bright AGN (see
section~\ref{systematic_errors_on_extension}). Finding that the AGN we
test are not extended is not surprising.  This validation analysis is
not suitable to reject any hypotheses about the existence of mpc-scale
halos around AGN.

@@

Nine extended sources not included in 2FGL were found using this search.
Three were found in our search using 1-100 \gev photons and six were
found in our search using 10-100 \gev photons.  The fit properties of
these nine sources is summarized in table~\ref{new_ext_srcs_table}.
This table includes for each source the best fit position, extension,
spectrum, source significance, and significance of extension.

The results of our investigation of systematic uncertainties of this
measurement are presented in table~\ref{dual_localization_results}
and~\ref{alt_diff_model_results}.  Table~\ref{dual_localization_results}
shows a comparison between the fit with a single extended source
hypothesis and the fit assuming the emission originates from two
independent sources.  Table~\ref{alt_diff_model_results} shows the
results of the extension fit using variations of the PSF and the galactic
diffuse model described in section~\ref{systematic_errors_on_extension}.
There is good agreement between \tsext and the fit size using
the standard analysis, the alternative diffuse models, and the alternative PSF.
This suggests that the sources are robust against features in the diffuse
model and uncertainties in the angular resolution.

@@

The source 2FGL\,J0823.0-4246 was found 
using 1-100 \gev photons to have an 
extension of $0.37\deg\pm0.03\deg_\stat\pm0.02\deg_\sys$ 
with an extension
significance of $\tsext=46.3$.  The source was fit to a position of
$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source.  This source is coincident with the one year
catalog source 1FGL\,J0823.3-4248.

@@

The source 2FGL\,J1627.0-2425c was found 
using 1-100 \gev photons to have an 
extension of $0.41\deg\pm0.05\deg_\stat\pm0.02\deg_\sys$ 
with an extension significance of $\tsext=31.1$. 
The best fit position is $(l,b)=(353.08\deg, 16.78\deg)$.
This source is coincident with the one year catalog source 1FGL\,J1628.6-2419c.
A counts map showing this source is
seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=20.0$
is smaller than \tsext, we conclude that this is an extended source.

@@

The source 2FGL\,J1712.4-3941 was found using 1-100 \gev
photons to have an extension $0.56\deg\pm0.04\deg_\stat\pm0.02\deg_\sys$
with an extension significance of $\tsext=39.6$.  This source was
fit to a position of $(l,b)=(347.25\deg,-0.54\deg)$.  The source
is coincident with the one year catalog source 1FGL\,J1711.7-3944c.
Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.

@@

The source 2FGL\,J0851.7-4635 was found 
using 10-100 \gev photons to have an
extension of $1.13\deg\pm0.08\deg_\stat\pm0.05\deg_\sys$ 
with an extension
significance of $\tsext=87.2$.  The source was fit to a position of
$(l,b)=(266.29\deg,-1.43\deg)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

@@

To get a good fit of the source, we had to remove thee nearby catalog
sources 2FGL\,J0853.5-4711, 2FGL\,J0848.5-4535, and 2FGL\,J0855.4-4625
which are part of the extended source.  In addition, we relocalized
the position of the nearby catalog source 2FGL\,J0854.7-4501 to
$(l,b)=(266.24\deg,0.49\deg)$ to better fit its position at high energies
in the presence of of the extended source.  In addition, we removed the
further away catalog sources 2FGL\,J0858.0-4815 and 2FGL\,J0901.7-4655
because they were not significant above 10 \gev.  After modifying
the region, we found that \tsinc=16.1 which is less than \tsext so we
conclude that the source is extended.

@@

The source 2FGL\,J1615.0-5051 was found using 10-100 \tev
photons to have an extension of $0.33\deg\pm0.04\deg_\stat\pm0.01\deg_\sys$
with an extension significance of \tsext=16.3.  The source
was fit to a position of $(l,b)=(332.38\deg,-0.14\deg)$.
This source is coincident with the one year catalog source
1FGL\,J1613.6-5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
of this source.

@@

2FGL\,J1615.2-5138 is spatially coincident with the extended
\tev source HESS\,J1616-508 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616-508 are overlaid
on 2FGL\,J1615.0-5051.  The H.E.S.S. experiment measured a Gaussian
extension $0.136\pm 0.008$ when fitting the source with an elliptical
Gaussian surface brightness.  This size corresponds to a 68\% containment
radius of $\rsixeight=0.21\deg\pm0.01\deg$. This size is comparable to the LAT
size $\rsixeight=0.27\deg\pm0.03\deg$ (see section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0-5051
connects smoothly to the H.E.S.S spectrum of HESS\,J1616-508.

@@

The source 2FGL\,J1615.2-5138 was found using 10-100 \gev
photons to have an extension of $0.42\deg\pm0.03\deg_\stat\pm0.01_\sys$
with an extension significance of \tsext=48.0.  The source was fit to a
position of $(l,b)=(331.66\deg,-0.66\deg)$.  This source is coincident
with the one year catalog source 1FGL\,J1614.7-5138c.  Because 2FGL
J1615.2-5138 is close to 2FGL\,J1615.0-5051, the same model described
in section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
sources. Both sources can be seen in figure~\ref{1FGL_J1613.6-5100c}.
For 2FGL\,J1615.2-5138, \tsinc=37.0 which is less than \tsext so we
conclude that the source is extended.

@@

The source 2FGL\,J1632.4-4753c was found 
using 10-100 \gev photons to
have an extension of $0.44\deg\pm0.04\deg_\stat\pm0.03\deg_\sys$ 
with an extension
significance of \tsext=64.5.  The source was fit to a position of
$(l,b)=(336.41\deg,0.22\deg)$.  This source is coincident with the one
year catalog source 1FGL\,J1632.9-4802c.  Figure~\ref{1FGL_J1632.9-4802c}
shows a counts map of this source.

@@

This extended source is spatially coincident with the extended
\tev source HESS\,J1632-478 (\cite{hess_plane_survey}).  In
figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632-478 are
overlaid on 2FGL\,J1635.4-4717c.  H.E.S.S measured a Gaussian extension of
$\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the semi-major and semi-minor
axes when fitting the source with an elliptical Gaussian surface 
brightness.
This corresponds to a 68\% containment size $\rsixeight=0.31\deg\pm0.08\deg$
and $0.09\pm0.06$ along the semi-major and semi-minor axis. This
size is consistent with the LAT size $\rsixeight=0.36\deg\pm0.04\deg$.
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1635.4-4717c
connects smoothly to the H.E.S.S spectrum of HESS\,J1632-478 and most
likely corresponds to the same emission process.

@@

The source 2FGL\,J1837.3-0700c was found 
with 10-100 \gev photons 
to have an extension
of $0.35\deg\pm0.08\deg_\stat\pm0.03\deg_\sys$ 
with an extension
significance of $\tsext=18.8$.  The source was fit to a position of
$(l,b)=(25.08\deg,0.13\deg)$.  This source is coincident with the one
year catalog source 1FGL\,J1837.5-0659c.  Figure~\ref{1FGL_J1837.5-0659c}
shows a counts map of this source.

@@

      \tsext was computed with \gtlike assuming the best fit radially
      symmetric uniform surface brightness from \pointlike.  \glon and \glat are Galactic

@@

      $\sigma$ is the edge of the best fit radially
      symmetric uniform surface brightness model.

@@

      Lobes were not fit by our analysis but are include for completeness
